\chapter{Conclusions and Directions for Future Work}
\label{chap:conclusions}
\section{Summary of Main Conclusions of this Thesis}
\subsection{Impact of Magnetospheric System Size on Large-Scale Structure and Dynamics}
% TBD: 
In this thesis we have studied in detail how the large-scale structure and dynamics of Saturn's magnetosphere varies with system size. In Chapter~\ref{chap:compress}, we used the UCL/AGA model to investigate specifically how the compressibility of the magnetosphere varied with system size, and in Chapter~\ref{chap:LTsectors} we looked at how the large-scale structure varied at different system sizes across a range of local times. The size of the magnetosphere is in turn influenced by the upstream solar wind conditions; in Chapter~\ref{chap:intro} we discussed how the magnetopause location is determined to the first order by pressure balance between the solar wind dynamic pressure $D_\mathrm{P}$ and the internal magnetospheric plasma and magnetic pressures, and how $D_\mathrm{P}$ varies with both the density and speed of the solar wind plasma.

Our modelling results presented in Chapters~\ref{chap:compress} and \ref{chap:LTsectors} suggest that the large-scale structure of Saturn's magnetosphere is more disc-like when the system is expanded, beyond a sub-solar magnetopause radius of ${\sim}\SI{25}{R_S}$. This \textit{magnetodisc} configuration is associated with more radially stretched field lines in the middle magnetosphere near the equatorial plane around a thin equatorial current sheet, and a total magnetic field strength that falls more slowly with radial distance than a dipole magnetic field. If the system is compressed by increasing solar wind dynamic pressure, the magnetospheric magnetic field then reconfigures into a more dipolar structure, with a correspondingly thicker equatorial current sheet. 

Similar results were found in the empirical study by \citet{arridge2008}, based on \textit{Cassini} magnetic field observations. In that study, the authors surveyed \textit{Cassini} magnetometer data for current-sheet-like fields, and examined the distribution of observations that fit a certain set of criteria related t o magnetic field strength and orientation, which corresponded to a distorted, stretched magnetic field configuration. They found that a significant magnetodisc structure only formed on the dayside when the system was expanded with a sub-solar radius beyond ${\sim}{23}{R_S}$, and that for smaller systems, a magnetodisc only formed on the nightside and flanks. They suggested that this is due to the near-coincidence of the expected inner boundary of the magnetodisc based on stress balance, and the nominal subsolar magnetopause, meaning the disc is prevented from forming under compressed conditions. This is in agreement with the results of the study by \citet{bunce2008}, based on models of the ring current from \citet{bunce2007}, which found that the magnetic moment of the ring current increases as the system expands, causing a more extreme distortion of the magnetospheric magnetic field in such conditions. This behaviour was also confirmed in the original UCL/AGA model study based on a comparison of two models calculated at different sizes \citep{achilleos2010a}.

In a steady-state system, we can consider this reconfiguration from a dipolar to a more disc-like structure in the context of the force balance in the rotating plasma of the magnetosphere, between the centrifugal force, plasma pressure gradient force and `$\boldsymbol{J}\times\boldsymbol{B}$' Lorentz body force. In Section~\ref{intro:sec:plasmaforces} we showed how this Lorentz body force is equivalent to the sum of a magnetic pressure gradient force, and a magnetic tension force. Near the equatorial plane, the main force acting radially inwards is the component of the magnetic tension force perpendicular to the magnetic field, which is proportional to $B^2/r_\mathrm{c}$ (where $r_\mathrm{c}$ is the magnetic field line radius of curvature). As the system expands, the magnetic field strength in the outer magnetosphere falls, and so in order for the magnetic tension force to balance the centrifugal and plasma pressure gradient forces acting radially outwards, the radius of curvature of the magnetic field lines must decrease. This corresponds to a more disc-like magnetic field structure, supported by a thin sheet of azimuthal current that extends far into the outer magnetosphere. 

This aspect of magnetodisc structure  becomes particularly important when investigating how Saturn's magnetospheric structure varies with local time. The nominal magnetodisc is significantly larger on the nightside and flanks of the magnetosphere than on the dayside. In addition, recent results from \citet{pilkington2015b} suggest a small dawn-dusk asymmetry in the typical magnetopause radius. In Chapter~\ref{chap:LTsectors}, we presented results of a modelling study which suggested that this variation in system size did indeed influence the magnetic field structure at different local times, which in turn influences magnetic mapping between the equatorial disc and the ionosphere. We found that in particular the open-closed field line boundary mapped to more equatorial regions of the ionosphere for the nightside and flanks than on the dayside, with a small dawn-dusk asymmetry, which has impacts for interpreting ionospheric phenomena such as aurora, as discussed in that chapter.

In Chapter~\ref{chap:equinox} we used a family of UCL/AGA models calculated with different radii in the range $45{\--}\SI{55}{R_S}$, and organised with Saturnian `longitude',  to simulate a periodic thickening and thinning of Saturn's magnetospheric current sheet in response to the dual rotating magnetic perturbations discussed in Section~\ref{intro:sec:periodicities}. We found that, when combined with a geometrical model of a tilted and rippled current sheet surface, this model characterised well the observed periodic perturbations in the magnetic field measured by \textit{Cassini} in Saturn's outer magnetosphere. In particular we found that the meridional component of  the magnetic field was much better characterised when this thickness perturbation in the magnetodisc was included. This suggests that our approach of using an oscillating boundary location with a $\SI{10}{R_S}$ range in disc radius appropriately simulates the corresponding change in magnetodisc structure and current sheet thickness, although with caveats as discussed in Chapter~\ref{chap:equinox}. Evidence for periodic perturbations in  the magnetopause boundary was found in the empirical study by \citet{clarke2010}, and also the MHD modelling study of \citet{kivelson2014}. In Chapter~\ref{chap:equinox} we found significant variation in the estimated phase of rotation at which we expected the maximum displacement of the magnetopause boundary (the parameter $\lambda_\mathrm{B}$) between the \textit{Cassini} passes studied. This suggests this relationship varies on short time scales, corresponding  to the phase relationship between the northern and southern hemispheric magnetic perturbations that contribute to this behaviour. Potential improvements to this study in particular are discussed later in this chapter, in Section~\ref{conclusions:sec:perturbations}.

This reconfiguration of the magnetic field under compressed conditions also influences the compressibility of Saturn's dayside magnetosphere in response to changing solar wind dynamic pressure. The compressibility itself is a quantitative indication of the degree to which the magnetodisc current affects the total magnetospheric field. In Chapter~\ref{chap:compress} we presented results of a modelling study which suggested that the magnetosphere becomes more easily compressible as it expands, due to the more significant magnetodisc structure under such conditions. As previously mentioned, a more significant magnetodisc structure has a magnetic field profile  with strength varying more slowly with radial distance than a  dipole, due to the magnetic field associated with the azimuthal ring current. This affects the pressure balance between the magnetic pressure and the solar wind dynamic pressure at the magnetopause boundary, and thus the associated compressibility, making the magnetosphere size more sensitive to a given change in solar wind dynamic pressure. A similar result was found in the aforementioned ring-current modelling study of \citet{bunce2007}, due to similar arguments of the magnetodisc structure becoming more significant for an expanded system.

We showed in Chapter~\ref{chap:compress} that this behaviour at Saturn contrasts with the Jupiter system, which seems to show a magnetospheric compressibility behaviour that is approximately constant across system size. We suggested that this was because, unlike the case of Saturn, Jupiter's magnetosphere has a consistent magnetodisc magnetic field structure across the full range of observed system sizes, even when extremely compressed under the high solar wind pressure conditions typically observed. Therefore the magnetic pressure, which dominantly controlled the compressibility in our UCL/AGA modelling results, varies self-similarly with radial distance for the different system sizes. This more stable and persistent magnetodisc structure at Jupiter is due to a range of factors, first discussed in Section~\ref{intro:sec:comparativemagnetospheres}. Jupiter has a more significant internal source of plasma than Saturn, originating from the volcanic moon Io, and also rotates more rapidly, with a $\SI{9.9}{\hour}$ period compared to Saturn's  ${\sim}\SI{10.6}{\hour}$. In addition, the overall size-scale of Jupiter's magnetosphere is  greater, with typical magnetopause stand-off distance of ${\sim}\SI{75}{R_J}$, due to the larger interior magnetic field at Jupiter (details in Table~\ref{intro:table:magnetospherecomparison}), and the pressure of the internal plasma population. Therefore the centrifugal force exerted radially outwards on the magnetospheric plasma is greater at Jupiter than at Saturn, causing a more significant distortion of the magnetic field into a magnetodisc structure, supported by an intense ring current \citep[e.g.][]{khurana2004}. As a consequence, Jupiter's magnetosphere has a more stable magnetodisc structure, particularly on the dayside when compared to Saturn, despite being significantly closer to the Sun and therefore experiencing higher average solar wind dynamic pressures. In contrast, if Saturn were located at Jupiter's position in the solar system, it would show a uniform compressibility behaviour across system size, specifically corresponding to its compressed, more rigid regime. Therefore the impact of varying system size on the large-scale structure and dynamics of each planetary magnetosphere also depends on both internal and external influences.

\subsection{Impact of Hot Plasma Population on Large-Scale Structure and Dynamics}
In this thesis we have also investigated in detail how the large-scale structure and dynamics of Saturn's magnetosphere are influenced by the presence of an internal, global hot plasma population. It is pertinent to study the impact of this population in particular as observational studies have shown that this population varies significantly over short timescales \citep{sergis2011} and in local time \citep{sergis2017}, suggesting that its influence may also vary across these domains. This is in contrast to the more stable population of cold plasma originating from Saturn's icy moon Enceladus, which is confined towards the equatorial plane due to the centrifugal force acting on it, and thus consistently contributes to the formation of a magnetodisc structure in a reasonably predictable way \citep[e.g.][]{arridge2008}. 

In addition, due to the local and global variability in the hot plasma population, it is difficult to study its impact on magnetodisc structure based on \textit{in situ} measurements alone, as a local measurement of plasma properties does not necessarily reveal information about the large-scale distribution of plasma throughout the magnetosphere. The UCL/AGA model is therefore particularly well suited to use as a tool to investigate this issue, as the hot plasma pressure throughout the magnetosphere can be simply parameterised in the model, in line with the expected range based on \textit{in situ} observations, and the corresponding effect on the magnetodisc structure can thus be readily investigated. 
%This is in contrast to MHD modelling studies such as \citet{jia2012b}, which do not account for a suprathermal plasma pressure population in their model construction.

In Chapters~\ref{chap:compress} and \ref{chap:LTsectors}, we presented results which suggest that, in general, a globally enhanced hot plasma pressure causes a more disc-like magnetic field structure, with more radially stretched magnetic field lines in the middle and outer magnetosphere. A similar result was found in \citet{achilleos2010b}, who compared two UCL/AGA models calculated with different hot plasma states. This reconfiguration is due to the enhancement of the equatorial ring current intensity associated with an increased energetic particle pressure, and the associated magnetic field becoming more distorted from a dipole under such conditions. This enhancement in the ring current intensity, and associated influence on the magnetodisc structure, is demonstrated explicitly in Chapter~\ref{chap:LTsectors}. There we compared results of UCL/AGA models representing different local time sectors, using different typical hot plasma pressure profiles as inputs based on observations from \citet{sergis2017}, who found that, in general, the pressure associated with the hot plasma population was greater in the dusk and night local time sectors compared to noon and dawn. We found that this produced corresponding variations in the equatorial profiles of magnetic field strength for each local time sector; of particular interest perhaps was a small asymmetry between dawn and dusk, with higher magnetic field strength in the middle and outer magnetosphere in general at dusk, which would be unlikely to reveal itself in often perturbed \textit{in situ} magnetic field observations. This hot plasma pressure asymmetry also caused a more distorted magnetodisc structure with thinner current sheet at the dusk sector under certain conditions; however due to the aforementioned dawn-dusk asymmetry also in system size, this effect was comparable to the more disc-like structure generated at dawn under certain conditions, due to the larger system size there. Different mechanisms promote a disc-like structure at the dawn sector (larger magnetopause radius) and the dusk sector (enhanced hot plasma pressure), and so we found that in general the asymmetry between them was small, and depended on the overall size of the magnetosphere. Similarly the mapping of field lines between the equatorial disc and the ionosphere showed some sensitivity to the hot plasma content, but in general was more sensitive to changes in system size, which also varied with local time.

In terms of dynamics, in Chapter~\ref{chap:compress} we showed that the hot plasma population also influenced magnetospheric compressibility, increasing the sensitivity of the magnetospheric size to changing solar wind conditions. This influence was comparable to the change in compressibility across t he typical range of observed system sizes. This is partially explained by the aforementioned reconfiguration of the magnetospheric magnetic field in such conditions, with associated magnetic field pressure varying more slowly with radial distance for systems with higher hot plasma content, and therefore being more easily compressible. However we also showed that, in our UCL/AGA model calculations, for a magnetosphere with sufficiently high hot plasma content (still in line with observations from \citet{sergis2007}), the plasma $\beta$ associated with the hot plasma population at the boundary surpassed unity. This means that, under such conditions, the behaviour of the hot plasma pressure, and how it varies with radial distance, becomes very important in determining pressure balance at the magnetopause boundary, and thus controlling magnetospheric compressibility. We found that the hot plasma pressure typically varied even more slowly with radial distance than the magnetic pressure associated with a magnetodisc field structure, and thus the magnetosphere became more easily compressible under such conditions. A recent empirical study of the size and shape of Saturn's magnetopause boundary by  \citet{pilkington2015}, also found evidence that the magnetospheric compressibility behaviour was influenced by the magnetosphere's internal plasma state. However as thoe authors were limited to using single-point \textit{in situ} observations of magnetospheric conditions, they could only investigate the relationship with the local plasma $\beta$ measured at the magnetopause crossing location, rather than the global state of the hot plasma population in the magnetosphere.

\section{Possible Directions for Future Work}
\subsection{Modifications to the UCL/AGA Magnetodisc Model}
The UCL/AGA model from \citet{achilleos2010a} has been a key tool for investigating the large-scale structure of Saturn's magnetosphere in this thesis. In Chapter~\ref{chap:compress}, we made calculations of the UCL/AGA model over a wider range of parameter space than in previous studies \citep{achilleos2010a, achilleos2010b}, varying both the system size and global hot plasma content to more extreme values, which were still consistent with the observed variability. This allowed us to explore in more detail how the behaviour of Saturn's magnetosphere varied across this parameter space. In Chapter~\ref{chap:equinox}, we further extended the applicability of the UCL/AGA model, using a family of models at different sizes to represent a magnetosphere with a periodically oscillating magnetopause boundary, and mainly investigating the dusk flank. For this study we needed to make calculations with larger disc radii than in previous studies, of $\SI{45}{R_S}$ and above, and in our research found that a number of modifications were needed to successfully use the UCL/AGA model in this way. In particular adapted the `shielding field' component of the magnetic field, to account for the larger magnetopause `fringing field', and also modified the way in which the model approaches convergence, in order to be able to  produce converged equilibria at the larger disc radii we explored. We also updated the equatorial profile of angular velocity used as a boundary condition in the model, as described in Section~\ref{appendix:sec:wilsonfits}. In Chapter~\ref{chap:LTsectors}, we then extended the applicability of the  UCL/AGA model further still, by making adaptations such that it could be used to represent different local time sectors. We again modified the shielding field component calculation, used local-time-sector-specific hot plasma pressure profiles as boundary conditions, and also updated the equatorial profile of ion temperatures used as boundary conditions, described in Section~\ref{appendix:sec:wilsonfits}. In this way, we have shown how the UCL/AGA model can be adapted and used to investigate a variety of different phenomena at Saturn.

The study in Chapter~\ref{chap:LTsectors}, in particular, demonstrated the possibility of effectively extending the UCL/AGA model beyond its original 2-D construction. Further to this, the equatorial profiles of other plasma properties used as boundary conditions in the model could also be made local-time-sector-specific, or otherwise updated using recent results based on \textit{Cassini} observations. For example, the survey of CAPS data from \citet{wilson2017}, which was used to update the plasma angular velocity and temperature profiles, also provides binned observations of temperatures and number densities for hydrogen and water group ions, separated into four local time sectors, as in our study. The results presented in \citet{wilson2017} do not show a significant local time asymmetry in these properties, and are also somewhat limited by the lack of data in the dawn sector due to irregular sampling by \textit{Cassini}. However these observations could still be used to constrain, for example, how the cold plasma population distribution varies with local time, which may have some impact on the variations in magnetodisc structure we saw in Chapter~\ref{chap:LTsectors}. If possible, observations used to inform plasma boundary conditions could be restricted to even more limited local time sectors with 2 or $\SI{4}{\hour}$ widths, in order to investigate with `higher resolution' how the magnetodisc structure varies across local time. However the aforementioned incomplete sampling of \textit{Cassini} may make this approach difficult in some regions of the magnetosphere. In addition, the minimum azimuthal resolution must remain large enough to justify the axisymmetric approximation used in the model construction.

One limitation of the UCL/AGA model is that it assumes the plasma pressure is isotropic, as discussed in Section~\ref{intro:sec:forcebalancemodel}.  This means the model does not account for any resultant force on the plasma associated with the anisotropy of the plasma pressures parallel and perpendicular to the curved magnetic field lines. As the azimuthal currents in the UCL/AGA model are calculated based on the assumption of force-balance (see equation~\ref{intro:eq:forcebalance}), the model therefore does not account for any contribution to this current associated with the pressure anisotropy. Empirical studies based on \textit{Cassini} CAPS data such as \citet{sergis2010} and \citet{kellett2011} found that the current associated with pressure anisotropy is significant particularly in the inner magnetosphere inside ${\sim}10{\--}\SI{12}{R_S}$, where $P_\perp > P_\parallel$, and that this current flows in the opposite direction  to planetary rotation, and therefore opposite to main ring current associated with centrifugal force on the plasma in this region. In this thesis we have mainly  used the UCL/AGA model to investigate Saturn's middle and outer magnetosphere beyond this region, and so our results are unlikely to be affected by this assumption of plasma isotropy. However an adaptation to the model to include pressure anisotropy may benefit future studies. A recent study by \citet{nichols2015} used a similar model construction to \citet{achilleos2010a}, also based on \citet{caudal1986}, to investigate Jupiter's magnetodisc, and found that pressure anisotropy currents were significant in Jupiter's middle magnetosphere in particular, and gave better overall agreement with \textit{in situ} plasma data than an earlier model \citep{nichols2011} that did not include the effects of pressure anisotropy.

An improved UCL/AGA model that can more accurately describe the structure of Saturn's magnetodisc at different local times and under different conditions, could be useful for many future investigations of Saturn's magnetosphere. For example, a model for  mapping magnetic field lines from the equatorial disc to the ionosphere under  different conditions could be useful for investigating ionospheric phenomena such as aurora, and for investigating the relationship between plasma properties at high latitudes and the equator as in \citet{sergis2018}. As an extension to the study  in Chapter~\ref{chap:equinox}, we could construct a  more physically realistic family of models to represent the periodic perturbation of the magnetopause boundary, that would be applicable to other datasets with different ranges in local time.

\subsection{Improved Studies of Periodic Perturbations in Saturn's Current Sheet}\label{conclusions:sec:perturbations}
The periodic perturbations in the position and the thickness of Saturn's equatorial current sheet, discussed in Chapter~\ref{chap:equinox}, are still actively being investigated in the community. In particular there is still a great deal of research ongoing into the nature of the rotating magnetic perturbations discussed in Section~\ref{equinox:sec:intro}, associated with hemispheric field-aligned current systems located at ${\sim}\SI{12}{R_S}$, and which appear to cause this periodic behaviour of the current sheet in the outer magnetosphere. In fact, since the study in Chapter~\ref{chap:equinox} was completed, the picture of the two magnetic perturbations being approximated by rotating transverse dipoles, as shown in Figure~\ref{equinox:fig:CowleyTDdiagrams}, has been further developed into a more complicated picture \citep[][Figure 13]{provan2018}. This and other studies, such as \citet{dougherty2018}, have employed the unique and powerful datasets measured during \textit{Cassini's} Grand Finale orbits (discussed in Section~\ref{cassini:sec:timeline}) to learn more about the nature of Saturn's magnetic field. It is therefore a particularly exciting time for this area of research.

There are numerous ways in which the study presented in Chapter~\ref{chap:equinox} could be taken further. As discussed in that chapter, the family of UCL/AGA magnetodisc models used  to simulate the breathing behaviour did not represent a system under constant solar wind dynamic pressure, and also did not account for any local time variation in magnetodisc structure. We have developed our understanding of the second issue  in particular with our study in Chapter~\ref{chap:LTsectors}, and therefore it may be possible in future to construct a more realistic family  of models, or otherwise vary the coordinate system with which the models are sampled as discussed in Section~\ref{equinox:sec:conclusions}, in order to account for a local time variation in current sheet structure. This would allow the combined flapping and breathing model to be applied to other \textit{Cassini} trajectories, where the range in local time may be wider than the relatively small window we investigated in Chapter~\ref{chap:equinox}.

In addition, the flapping and breathing  model did not explicitly account for the phase difference between the northern and southern magnetic perturbations as it was beyond the scope of that study, and instead organised the model with  respect to the southern magnetic perturbation from \citet{andrews2012}. On publication of the study in \citet{sorba2018}, Stan Cowley at the University of Leicester suggested that we could attempt to account for the influence of both the northern and southern perturbations directly by simply summing terms representing the flapping (equation~\ref{equinox:eq:zcs}) and breathing (equation~\ref{equinox:eq:RD}) modes, for both northern and southern perturbations. In this construction, the values for the flapping and breathing parameters could be fixed following theoretical expectations from \citet[e.g.][]{cowley2017a} and discussed in Section~\ref{equinox:sec:intro}, with $\lambda_0 = \SI{180}{\degree}$ for both the northern and southern perturbations, and $\lambda_\mathrm{B}=\SI{0}{\degree}$ for the northern and $\SI{180}{\degree}$ for the southern perturbations. In addition, the amplitude of the northern and southern perturbations were nearly equal during the period near equinox studied in  Chapter~\ref{chap:equinox}. This further simplifies the construction as the relative amplitudes of the perturbations do not need  to be accounted for when investigating this interval specifically. This simplification would significantly reduce the number of parameters  in the combined flapping and breathing model. This would perhaps enable  us to strengthen the conclusions made in Chapter~\ref{chap:equinox}, and also potentially investigate, for example, the behaviour of the wave parameter $D=\Omega_\mathrm{S}/v_\mathrm{W}$, which controls how the information about  the magnetic perturbations propagates to the outer magnetosphere. In our study we used a fixed value of $D=\SI{3}{\degree \per R_S}$ due to the constraints of fitting several free parameters, but it would be interesting to investigate how this parameter may vary with radial distance and local time, especially as some other studies looking into these periodic phenomena have also assumed a fixed value of $D$. In addition, we could potentially introduce a parameter to control the variation in current sheet thickness, by varying the range in disc model radii $R_\mathrm{D}$ between passes, rather than using a fixed range of $45{\--}\SI{55}{R_S}$. This would enable an investigation of how  the current sheet thickness modulation  varies with phase difference between the magnetic perturbations.

\subsection{Looking Further Ahead}
We have mentioned how, with the end of the \textit{Cassini} space mission in September 2017, it is currently a particularly exciting time for this area of research. Comprehensive investigations of the large-scale structure of Saturn's magnetosphere are now being completed \citep[e.g.][]{sergis2017,wilson2017}, which wouldn't have been possible even a few years ago, due to data limitations. In addition,  observations made during \textit{Cassini's} Grand Finale orbits have revealed information about Saturn's internal magnetic field and interior structure, which are still not fully understood \citep[e.g.][]{dougherty2018}. 

However, it is also important that we look forward to the next scientific frontier, in preparation for when the legacy \textit{Cassini} science dataset has been fully exploited. In particular, throughout this thesis we have often compared results and interpretations of Saturn's magnetosphere to those of Jupiter, as the two planets bear both similarities and differences in their structures and dynamics (planetary \textit{sisters} rather than \textit{twins}). It is therefore pertinent to consider future research in this area of Jupiter magnetospheric science. NASA's \textit{Juno} space mission to Jupiter \citep{bolton2017} entered into orbit around the planet in July 2016, and will continue to make repeated highly elliptical, polar orbits of the planet until planned mission close-out in July 2021. These polar orbits have a closest approach of $\sim\SI{1.05}{R_J}$ and a furthest distance of $\sim\SI{38}{R_J}$, and are constrained to the planet's dawn flank \citep{bagenal2014}. Therefore there is limited opportunity to investigate local time variation in large-scale structure, or periodic dynamics of the equatorial current sheet, as we have conducted in this thesis for Saturn. However a few magnetopause crossings were observed by the spacecraft during the initial larger capture orbit, and have been used to investigate the size and shape of Jupiter's magnetopause surface particularly on the dawn flank \citep{gershman2017}. Due to the relatively long (${\sim}{53}$ day) orbit of \textit{Juno}, it will perhaps be  a while yet before a conclusive dataset is gathered, which can be used for more comprehensive studies. 

Looking further ahead still, ESA's JUpiter ICy Moon Explorer (\textit{JUICE}) mission to Jupiter \citep{grasset2013} is set for launch in June 2022, to enter orbit  around the planet in October 2029. Over the total planned mission of ${\sim}3.5$ years (not including the time of  transit to Jupiter), \textit{JUICE} will explore Jupiter and its moons Ganymede, Europa and Callisto, and will even enter orbit around Ganymede in the later stage of the mission. The \textit{JUICE} trajectory around Jupiter has been designed to more comprehensively investigate the Jovian magnetospheric environment, and will cover all regions of the equatorial magnetosphere out to at least $\SI{100}{R_J}$ \citep{esa2014}. This should enable a more comprehensive investigation of the compressibility of Jupiter's magnetosphere, and the magnetodisc structure at different local times. These results could then be used to put the work presented in this thesis for Saturn into a more global `planetary' context.
%
%
%
%
%%
%
%
%%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%